\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-18 notes/2loopNLSM.tex
Starting to think about abstract.
A few actual sentences in abstract.

\abstract{
\ace{I will start working here over the weekendish}

>>>>

\abstract{

  We catalog and analyze ?4? theories which all manifest the duality
  between color and kinematics both at tree and one-loop level.  We
  identify a unifying theory, \emph{semi-abelian} Yang--Mills, from
  which all four of the theories can be extracted.  Joint
  consideration of these theories sheds light on the long-standing
  problem.

  \begin{itemize}
  \item Catalog themes among ``manifestly'' color dual theories
  \item Identify obstructions going $1 \to 2$ loop
  \item Highlight obstructions and overcome via NLSM bootstrap
  \item Brief revisit of 2L YM
  \end{itemize}
